---
title: "acoustic_analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
verb column is actaully item

```{r}
features = c("duration", "meanIntensity", "meanpit")
info = c('participant','verb','condition', 'word', 'word_num')
bRemove_outliers = 0
library(dplyr)
library(lme4)
library(zeallot)
  library(Rmisc)
  library(ggplot2)
  library(plyr)

```

```{r}
gdata = read.csv("measure_nonrhyming_84total_60No_24Yes_20181210.csv", header  = T)
# gdata = transform(gdata,PresentationNum=as.numeric(PresentationNum))
# sort(gdata$PresentationNum, decreasing = FALSE)
colnames(gdata)

# code for word_num
new.df <- gdata %>% 
  dplyr::group_by(participant, question, presentationnum) %>%
  dplyr::mutate(word_num=1:dplyr::n()) %>%
  dplyr::select(c(info, features))

write.csv(new.df,'newdf.csv')
# code for getting Nth instance of question
# nthdf <- new.df %>%
#   group_by(participant,Verb, question, condition, word_num) %>%
#   mutate(Appearance=1:n())
#write.csv(nthdf,'nthdf.csv')

# subsetting it to relevant Nth appearance
# workingdf <- nthdf %>%
#   filter (Appearance == 2)
# 
# write.csv(workingdf,'workingdf2.csv')

normalize_data = function(df, remove_outliers){
  for(col_name in features){
    df[[col_name]] = scale(df[[col_name]])
    # there is surge of na after the first colling of the above line. tested by print(sum(is.na(df_Agent))). I guess it's because the df is nibble
        # print(sum(is.na(df_Agent)))

  }
  for(col_name in features){
    
    if(remove_outliers){
      df = df[df[[col_name]]>-2 & df[[col_name]]<2,]
          # print(sum(is.na(df_Agent)))

    }
  }
  return(df)
}

process_data = function(file_name){
  df <- read.csv(file_name,header = TRUE, fileEncoding="UTF-8",na.strings=c("", "NA","--undefined--"))
  df <- na.omit(df)
  
  #df = df[df$wordlabel != 'sp']
  # df$verb = as.factor(df$verb)
  
  
  # df_Agent = df[(df$condition=='Agent' | df$condition=='Verb') & df$word_num=='3',]
  # 
  # df_Verb = df[(df$condition=='Verb'| df$condition=='Patient') & df$word_num=='5',]
  # 
  # df_Patient = df[(df$condition=='Patient'| df$condition=='Agent') & df$word_num=='6',]
  
  df_Agent = df[(df$condition=='Agent' | df$condition=='YesControl') & df$word_num=='3',]
  # df_Agent inheri row hum from df
  
  df_Verb = df[(df$condition=='Verb'| df$condition=='YesControl') & df$word_num=='5',]
  
  df_Patient = df[(df$condition=='Patient'| df$condition=='YesControl') & df$word_num=='6',]
  
  # print(sum(is.na(df_Agent)))
  
  # relevant_columns = c('participant','verb','condition','duration','meanIntensity','meanpit')
  # df_Agent = df_Agent[relevant_columns]
  # df_Verb = df_Verb[relevant_columns]
  # df_Patient = df_Patient[relevant_columns]
  sum(is.na(df[new.df$word != 'sp',]))
  # new.df[(new.df$meanpit == '--undefined--') && (new.df$word != 'sp'),]
  # it seems that the only undefined is meanpitch for sp
  

  
  df_Verb = normalize_data(df_Verb, bRemove_outliers)
  df_Agent = normalize_data(df_Agent, bRemove_outliers)
  df_Patient = normalize_data(df_Patient, bRemove_outliers)
    # print(sum(is.na(df_Agent)))

  
  
  # return(list(df_Agent_duration, df_Agent_meanIntensity, df_Agent_meanpit, df_Patient_duration, df_Patient_meanIntensity, df_Patient_meanpit,df_Verb_duration, df_Verb_meanIntensity, df_Verb_meanpit))
  return(list(df_Verb, df_Agent, df_Patient))
}


```

```{r}

file_name = 'newdf.csv'

# c(df_Agent_duration, df_Agent_meanIntensity, df_Agent_meanpit, df_Patient_duration, df_Patient_meanIntensity, df_Patient_meanpit,df_Verb_duration, df_Verb_meanIntensity, df_Verb_meanpit) %<-%process_data(file_name)
c(df_Verb, df_Agent, df_Patient) %<-% process_data(file_name)


combine_datasets = function(Agent,Verb,Patient){
  Agent$condition = mapvalues(Agent$condition,c('Agent'),c('contrast'))
  Verb$condition = mapvalues(Verb$condition,c('Verb'),c('contrast'))
  Patient$condition = mapvalues(Patient$condition,c('Patient'),c('contrast'))
  
  Agent$Location = 'Agent'
  Verb$Location = 'Verb'
  Patient$Location = "Patient"
  
  return(rbind(Agent,Verb,Patient))
}

summarize_data = function(d, feature){
  # http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/
  return(summarySE(d,measurevar=feature ,groupvars=c('Location','condition')))
}
plot_data = function(d,feature, title){
  print(ggplot(d, aes(x=Location, y=get(feature), fill=condition)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=get(feature)-ci, ymax=get(feature)+ci),
                  width=.2,                   
                  position=position_dodge(.9))+
    xlab("Location") +
    ylab(paste0("normalized ", feature)) +
    scale_fill_hue(name="Condition", 
                   breaks=c("YesControl", "contrast"),
                   labels=c("NonContrastive", "Contrastive")) +
    ggtitle(title))
}
for (iF in features){
  print(iF)
  
  combined_dataset = combine_datasets(df_Agent, df_Verb, df_Patient)
  summarized_dataset= summarize_data(combined_dataset, iF)
  
  
  plot_data(summarized_dataset,iF, title= paste0('Effect of contrast on ', iF))
}

```


# ```{r, results="asis"}
```{r}
run_regression = function(location,observation){
cat("  \n###", observation, "of", location, "  \n")
    r = lmer(get(observation) ~ condition + (1 + condition|participant) + (1 + condition | verb), data=get(paste0("df_", location)))
  print(summary(r))
  summary(r)
  cat("  \n")
}



for (iF in features){
  run_regression("Agent",iF)

  
  run_regression("Patient", iF)

  run_regression("Verb", iF)

  
  
}
    r = lmer(get(observation) ~ condition + (1 | participant) + (1 | verb), data=df)

```

